\documentclass[12pt]{article}
\usepackage{amsmath, amssymb,amscd}
\usepackage{setspace}
\usepackage{enumerate}
\usepackage{verbatim,multicol}
\pagestyle{empty}
\setlength{\parindent}{0in}
\oddsidemargin 0in
\textwidth 6.5in
\topmargin 0in
\textheight 9in
\doublespace

\newcommand{\qed}{\hfill$\Box$}

\begin{document} 

As discussed in \cite{DzSh}, we have results in math. These results were originally formulated and proved in \cite{Ch}. However a shorter proof of the main result can be found in \cite[Theorem 3.4]{Wo}.

\begin{thebibliography}{9}
%
\bibitem{Ca}
E. Casanovas,
{\emph{NIP formulas and theories}},
Model Theory Seminar notes, 2010.\\\textit{http://www.ub.edu/modeltheory/documentos/nip.pdf}
%
\bibitem{Ch}
A. Chernikov,
{\emph{Theories without the tree property of the second kind}},
arXiv:1204.0832v3 [math.LO] (2013).
%
\bibitem{vdD}
L. van den Dries,
{\emph{Tame Topology and o-minimal Structures}},
London Mathematical Society Lecture Note Series 248, Cambridge, 1998.
%
\bibitem{DzSh}
M. D\v{z}amonja \& S. Shelah,
{\emph{On $\lhd^*$-maximality}},
Annals of Pure and Applied Logic 125 (2004) 119-158.
%
\bibitem{KiKi}
B. Kim \& H. J. Kim,
{\emph{Notions around tree property 1}},
Annals of Pure and Applied Logic 162 (2011) 698-709.
%
\bibitem{Me}
J. Melleray,
{\emph{Some geometric and dynamical properties of the Urysohn space}},
Toplogy and its Applications 155 (2008)  1531-1560.
%
\bibitem{MMP}
D. Marker, M. Messmer, \& A. Pillay,
{\emph{Model Theory of Fields, 2nd ed.}},
Cambridge, 2006.
%
\bibitem{Te}
K. Tent \& M. Ziegler,
{\emph{A Course in Model Theory}},
Cambridge, 2012.
%
\bibitem{Wo}
C. Wood,
{\emph{Notes on the stability of separably closed fields}},
Journal of Symbolic Logic 44 (1979) 412-416.
%
\end{thebibliography}


\end{document}
